---
title: "Cleansing Online Retails Dataset"
output: html_document
date: "2023-08-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is Data cleansing for online retails dataset from TATA online internship program.

## Importing data
```{r}
library("readxl")
Online_Retail_Data_Set<-read_excel("C:/Users/HP/Downloads/Online Retail Data Set.xlsx",)
```

## Sorting data to see what I should clean.
```{r}
Online_Retail_Data_Set[order(Online_Retail_Data_Set$UnitPrice),]
```
The original data contains negative unit price but we need only positive number in order to calculate the revenue. So, we select only positive unit price.

## Selecting only positive unit price.
```{r}
data<-subset(Online_Retail_Data_Set,UnitPrice>0)
data
```

## Adding the new column to calculate the revenue.
```{r}
library(dplyr)
data<- mutate(data,Revenue
              =data$Quantity*data$UnitPrice)
data
```

## Save cleaned data
```{r}
write.csv(data,"modified_online_sale.csv"
          , row.names = F)
```

